Distinct communities of snow algae bloom at different elevations

### 2019-10-24 doc/Casey1.Rmd
transfer files over from old rproj

Snow algae are cold-adapted microalgae that bloom in melting summer snow [@Leya2013]. Red pigments produced by some species of snow algae can color vast areas of polar and alpine snowfields, which decreases snow surface albedo---by one estimate, enough to substantially increase the rate of snow melt [@Ganey2017]. Depleted snowpack threatens water supplies and can lead to drought [@Staudinger2014;@Barnhart2016], and earlier snow melt exposes darker surfaces below, contributing to snow-albedo feedback and global warming [@Dery2007]; thus, snow algae could play an important role in snow melt regulation. Furthermore, snow algae are the primary producers in a microbiome that includes grazers, fungi, and bacteria [@Hoham2001], but whether there are ecological distinctions between types of snow algae blooms has been poorly studied. The first step in understanding this microbiome is defining the algae species that are present in snow algae blooms, and their community structure.

>>>>

Snow algae are cold-adapted microalgae that bloom in melting summer snow [@Leya2013]. Red pigments produced by some species of snow algae can color vast areas of polar and alpine snowfields, which decreases snow surface albedo---by one estimate, enough to substantially increase the rate of snow melt [@Ganey2017]. Earlier snow melt exposes darker surfaces below, contributing to snow-albedo feedback and global warming [@Dery2007], and loss of snowpack reservoirs can threaten water supplies, leading to drought [@Staudinger2014;@Barnhart2016]. Thus, snow algae could play an important role in snow melt regulation. Snow algae are the primary producers in a microbiome that includes grazers, fungi, and bacteria [@Hoham2001], but whether this microbiome can be considered as a single microbiome, or whether there are distinctions between types of snow algae blooms has been poorly studied. The first step in understanding this microbiome is defining the algae species that are present in snow algae blooms, and their community structure.
